&nbsp;

### 2021-03-19 inst/app/www/about.Rmd
updated UI and function documentation

The __SampleSizePlanner__ shiny application enables researchers to calculate the sample size with 8 different methods in app and provides code to use an additional method from R. The aim of the app is to make the various sample size calculating methods available for a wide range of researchers and propagate the transparent reporting of the choose method. Therefore, a formatted template text containing the used parameters and the output of the calculations is available for download. This text can be complemented with the reasoning behind each decision.

>>>>

The __SampleSizePlanner__ shiny application enables researchers to calculate the sample size with 9 different methods in app and provides code to use an additional method from R. The aim of the app is to make the various sample size calculating methods available for a wide range of researchers and propagate the transparent reporting of the choose method. Therefore, a formatted template text containing the used parameters and the output of the calculations is available for download. This text can be complemented with the reasoning behind each decision.
